\newcommand{\CapFigDatasetStats}{Regenerated dataset statistics for the three benchmarks (hourly train/validation/test split sizes).}
\newcommand{\CapTabHousehold}{Household Power Consumption benchmark results (CPU, mean$\pm$std over 5 seeds).}
\newcommand{\CapFigForecastUCI}{Four representative 24-hour forecasting cases on the UCI household benchmark using PGF-Net, DLinear, and S-Naive.}
\newcommand{\CapFigPeakUCI}{Regenerated predicted versus observed peak loads on the UCI household benchmark.}
\newcommand{\CapFigLatencyUCI}{Regenerated inference latency comparison across forecasting models (UCI benchmark setup).}
\newcommand{\CapFigWalkforwardUCI}{Horizon-wise MAE and MSE profiles over the current 30 UCI rolling-origin forecasts. Solid lines show horizon means and shaded bands show interquartile ranges across origins.}
\newcommand{\CapFigGateUCI}{Gate activations across 48 consecutive forecast origins on the UCI benchmark. Each column corresponds to the feature-wise gate vector generated from one 96-hour input window; the horizontal axis does not represent the 24-step output horizon. Quantitative gate summaries are reported in the current local package.}
\newcommand{\CapFigLoadUCI}{Grouped MAE and PLE summary across quartile-based low-, medium-, high-, and peak-load bins on the UCI benchmark.}
\newcommand{\CapTabWeekly}{Weekly Pre-dispatch benchmark results (same protocol, mean$\pm$std over 5 seeds).}
\newcommand{\CapTabKaggle}{Same-protocol \texttt{nat\_demand} benchmark results across all five models (mean$\pm$std over 5 seeds).}
\newcommand{\CapFigOverallThree}{Cross-dataset metric comparison (MSE, MAE, PLE) across UCI, Weekly Pre-dispatch, and Kaggle Nat Demand benchmarks under the same protocol, using dataset-specific subplot scales for readability.}
\newcommand{\CapFigForecastKaggle}{Regenerated 24-hour multi-step forecasting trajectories on the third public dataset (\texttt{nat\_demand}).}
\newcommand{\CapFigPeakKaggle}{Regenerated predicted versus observed peak loads on the third public dataset (\texttt{nat\_demand}).}
\newcommand{\CapFigHorizonKaggle}{Regenerated horizon-wise MSE comparison on the third public dataset (\texttt{nat\_demand}).}
\newcommand{\CapFigRobustKaggle}{Raw per-seed MSE comparison on the same-protocol \texttt{nat\_demand} benchmark across all five models after the fairness-stabilized DLinear rerun.}
\newcommand{\CapTabAblation}{Updated UCI ablation of PGF-Net and fusion variants (mean$\pm$std over 5 seeds).}
